---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# potemkin

<!-- badges: start -->
<!-- badges: end -->

The goal of potemkin is to raise a middle finger to the bureaucratization of science.

## Installation

You can install the development version of potemkin like so:

``` r
devtools::install_github("skvrnami/potemkin")
```

## Example

Does someone makes you fill pointless Excel spreadsheets with work report that no one will ever read but it is still required. No worries, `potemkin` package got you covered. Function `get_timesheet` will generate random distribution of your work hours into specified activity categories.

```{r example}
library(potemkin)

get_timesheet(c("admin", "research activities", "study of literature"), 
              n_hours = 40)

```

If you want to specify particular time spent on any activity, you can do so by using `specified_activities` parameter.

```{r}
get_timesheet(c("admin", "research activities", "study of literature"), 
              n_hours = 40, 
              specified_activities = list(meeting = 2))
```

